Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-26 papers/ms.tex
ms: push CH-2 and RSG-5 rotation periods

We define two sets of stars in the local vicinity of our objects of
interest, in order to verify whether they are indeed the same age.
For candidate RSG-5 members, we require:
\begin{align}
  45<X/{\rm pc}<75 \nonumber \\
  320<Y/{\rm pc}<350 \nonumber \\
  40<Z/{\rm pc}<70 \nonumber \\
  -4<v_b/{\rm km\,s^{-1}}<-3 \nonumber \\
  4<v_{l^*}/{\rm km\,s^{-1}}<6 \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
	20<X/{\rm pc}<70 \nonumber \\
	230<Y/{\rm pc}<270 \nonumber \\
	75<Z/{\rm pc}<105 \nonumber \\
	-3.5<v_b/{\rm km\,s^{-1}}<-1.5 \nonumber \\
	2<v_{l^*}/{\rm km\,s^{-1}}<6, \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.
% FIXME TODO numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv right now.  Can we do better?
These cuts yield 141 candidate RSG-5 members, and 
37 candidate CH-2 members.
Given the larger volume of the latter group, and the more diffuse base
sample of stars, a major concern is contamination by field stars.
We assess this in the following section.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.  The
    bottom left shows gyro (and is a {\bf place-holder since we might
    want to add CH-2 and RSG5}).  The bottom right shows lithium
    (black points are NGC2547 and IC2602 from Randich+18 and probably
    are not believable at the red end; for Kepler-1643 I'm less
    confident, but it might be tied to the ``slow'' rotation period --
    this is why we need RSG5 rotation periods).  Also, we might want
    an H-alpha plot?).
		\label{fig:age}
	}
\end{figure*}

>>>>

We define two sets of stars in the local vicinity of our objects of
interest, in order to verify whether they are indeed the same age.
For candidate RSG-5 members, we require:
\begin{align}
  45<X/{\rm pc}<75 \nonumber \\
  320<Y/{\rm pc}<350 \nonumber \\
  40<Z/{\rm pc}<70 \nonumber \\
  -4<v_b/{\rm km\,s^{-1}}<-3 \nonumber \\
  4<v_{l^*}/{\rm km\,s^{-1}}<6 \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
	20<X/{\rm pc}<70 \nonumber \\
	230<Y/{\rm pc}<270 \nonumber \\
	75<Z/{\rm pc}<105 \nonumber \\
	-3.5<v_b/{\rm km\,s^{-1}}<-1.5 \nonumber \\
	2<v_{l^*}/{\rm km\,s^{-1}}<6, \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.
% FIXME TODO numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv right now.  Can we do better?
These cuts yield 141 candidate RSG-5 members, and 
37 candidate CH-2 members.
Given the larger volume of the latter group, and the more diffuse base
sample of stars, an important concern is contamination by field stars.
We assess this in the following section.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.  The
    bottom left shows gyro (and is a {\bf place-holder since we might
    want to add CH-2 and RSG5}).  
    %The bottom right shows lithium
    %(black points are NGC2547 and IC2602 from Randich+18 and probably
    %are not believable at the red end; for Kepler-1643 I'm less
    %confident, but it might be tied to the ``slow'' rotation period --
    %this is why we need RSG5 rotation periods).  Also, we might want
    %an H-alpha plot?).
		\label{fig:age}
	}
\end{figure*}
